PRISM protocol v0.3

### 2021-10-29 prism-backend/research/article.tex

Assuming each participant of the system owns a (set of) DIDs, we want to let
holders receive new credentials from issuers, in a secure -- yet convenient --
manner. We describe a protocol for this purpose.  At the moment, we require
that issuer and prospective holder can perform a one-time physical interaction
with each other or, alternatively, that they have a secure channel at their
avail (although possibly cumbersome to use, hence we only require to use it
once).

In a nutshell, the proposed protocol (see \figref{fig:e2econnector}) is composed
of two phases. In the first phase, the issuer shares a QR code with the holder.
This QR code contains the issuer's public key (or, maybe, its DID), a random
value ($code$, in \figref{fig:e2econnector}), and a session identifier ($token$,
in \figref{fig:e2econnector}). This exchange takes place through a secure (i.e.,
confidential and authenticated) channel, such as physical exchange. Probably
immediately, although also possibly at a later point in time, the prospective
holder sends back her own public key (or, alternatively, her DID) and the
session identifier, all authenticated with a MAC, where we use the random value
in the QR code as secret key. The issuer uses the session identifier to locate
the corresponding session and, now that it received in an authenticated manner
the public key of the holder, can leverage hybrid encryption techniques to
establish an end-to-end encrypted session, e.g., using ECIES \cite{abr01}.
Ensuring end-to-end encryption and authentication is important at this point, as
all the information exchanged between issuer and holder is routed through the
connector: an entity or set of entities who ensure that asynchronous
communication can take place between issuer and holder. Thus, ECIES is crucial
to ensure the secrecy of the information, end-to-end. Since the holder needs to
have certainty that the data it receives comes from the issuer (and ECIES does
not authenticate the sender), we have the issuer digitally sign the data it
sends through the ECIES-secured channel. Note that we could involve the random
value shared via the QR code for this. But that would force us to re-execute the
first phase of the protocol even when the QR code is compromised after having
completed the first phase of the protocol. Digital signatures using the issuer's
DID prevent this.

>>>>

Assuming each participant of the system owns a (set of) DIDs, we want to let
holders receive new credentials from issuers, in a secure -- yet convenient --
manner. We describe a protocol for this purpose.  At the moment, we require
that issuer and prospective holder can perform a one-time physical interaction
with each other or, alternatively, that they have a secure channel at their
availability (although possibly cumbersome to use, hence we only require to use
it once).

In a nutshell, the proposed protocol (see \figref{fig:e2econnector}) is composed
of two phases. In the first phase, the issuer shares a QR code with the holder.
This QR code contains the issuer's public key (or, maybe, its DID), a random
value ($code$, in \figref{fig:e2econnector}), and a session identifier ($token$,
in \figref{fig:e2econnector}). This exchange takes place through a secure (i.e.,
confidential and authenticated) channel, such as physical exchange. Probably
immediately, although also possibly at a later point in time, the prospective
holder sends back her own public key (or, alternatively, her DID) authenticated
with a MAC, where we use the random value
in the QR code as secret key. The issuer uses the session identifier to locate
the corresponding session and, now that it received in an authenticated manner
the public key of the holder, can leverage hybrid encryption techniques to
establish an end-to-end encrypted session, e.g., using ECIES \cite{abr01}.
Ensuring end-to-end encryption and authentication is important at this point, as
all the information exchanged between issuer and holder is routed through the
connector: an entity or set of entities who ensure that asynchronous
communication can take place between issuer and holder. Thus, ECIES is crucial
to ensure the secrecy of the information, end-to-end. Since the holder needs to
have certainty that the data it receives comes from the issuer (and ECIES does
not authenticate the sender), we have the issuer digitally sign the data it
sends through the ECIES-secured channel. Note that we could involve the random
value shared via the QR code for this. But that would force us to re-execute the
first phase of the protocol even when the QR code is compromised after having
completed the first phase of the protocol. Digital signatures using the issuer's
keypair prevent this.
